---
title: "Case Study"
author: "Christopher Farrar"
date: "June 21, 2016"
output: 
     html_document:
     keep_md: true
---

## Case Study 

  * Will be reviewing Gross Domestic Product Data
    "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv" 
  
  * Education Data
     "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"

# This Case Study will be answering the following Questions.

  * Match the data based on the country shortcode. How many of the IDs match?
  
  * Sort the data frame in ascending order by GDP rank (so United States is last). What is the 13th 
    country in the resulting data frame?
    
  * What are the average GDP rankings for the "High income: OECD" and "High income: nonOECD" groups?
  
  * Plot the GDP for all of the countries. Use ggplot2 to color your plot by Income Group
  
  * Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many
    countries are Lower middle income but among the 38 nations with highest GDP

# Introduction
 This will present data of how GDP and education data go something....etc
 
```{r}

# First need to download the files

CaseStudy_1 <- read.csv("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv")
CaseStudy_2 <- read.csv("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv")

```

# Next will be the tidying and merging data code

```{r}

# first need to look at how it is set up
# This gets a look at the dimmesions of the data set
dim(CaseStudy_1)

# This gives us a quick summary of the data set
summary(CaseStudy_1)

# This looks at the data frame as well as create data frames
data.frame(CaseStudy_1)

# Also another function allows us to examine further the data frame
str(CaseStudy_1)

# After review of the GDP data, it apppears there were 6 columns with NA values that werent needed. So removed it
CaseStudy_1$X.1 <- NULL
CaseStudy_1$X.4 <- NULL
CaseStudy_1$X.5 <- NULL
CaseStudy_1$X.6 <- NULL
CaseStudy_1$X.7 <- NULL
CaseStudy_1$X.8 <- NULL

# Also realizing that X isn't really a good name decided to change the header
names(CaseStudy_1)[1] <- "CountryCode"
names(CaseStudy_1)[2] <- "Country"
names(CaseStudy_1)[3] <- "Economy"
names(CaseStudy_1)[4] <- "Millions"

# Also realizied there were some rows that didn't belong either

CaseStudy_1 <- CaseStudy_1[-c(1:4),]
CaseStudy_1 <- CaseStudy_1[-c(245:330),]

# Realized didnt need another variable
CaseStudy_1$Country <- NULL

# Wanted to completed the correct sorting
CaseStudy_1 <- CaseStudy_1[order(CaseStudy_1$CountryCode, CaseStudy_1$Economy, CaseStudy_1$Millions),]

# Lastly wanted to remove some rows again
CaseStudy_1 <- CaseStudy_1[-c(1:16),]

# Final Product of CaseStudy_1
CaseStudy_1

# Have to load the melt package "reshape2"
library(reshape2)

# This removes the NA values from CaseStudy_2 Variable
CaseStudy_2 <- melt(data = CaseStudy_2, na.rm = TRUE)

# Now going to merge the data
CaseStudy_3 <- merge(x = CaseStudy_1, y = CaseStudy_2, all = TRUE)

# Now going to see the case studies merged
names(CaseStudy_3)

```

# The code to answer the five questions

```{r}

# Question 1
str(CaseStudy_1)

# Based on the county code there are 239 values/countries

# Question 2
attach(CaseStudy_1)
Question2 <- CaseStudy_1[order(Millions),]
Question2
detach(CaseStudy_1)

# The answer is Bhutan

# Question 3
CaseStudy_2$Income.Group

# The average for HighIncome NonOECD is 52 Million and the average for HighIncome OECD is 148 Million

# Question 4
library(ggplot2)
ggplot(CaseStudy_3) + geom_bar(aes(Income.Group))

# Question 5...Couldn't get quantile to work right based on int vs factor data
CaseStudy_4 <- CaseStudy_3$value
quantile(CaseStudy_4, probs = seq(0, 1, 0.25), na.rm = TRUE, names = TRUE)

```

# Conclusion
 Enjoy the sweet sound of Case Study Music!

