---
title: "CaseStudy_Draft"
author: "Christopher Farrar"
date: "June 12, 2016"
output: 
     html_document:
     keep_md: true
---

## Case Study Draft

  * Will be reviewing Gross Domestic Product Data
    "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv" 
  
  * Education Data
     "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"

# This Case Study will be answering the following Questions.

  * Match the data based on the country shortcode. How many of the IDs match?
  * Sort the data frame in ascending order by GDP rank (so United States is last). What is the 13th country in the resulting
    data frame?
  * What are the average GDP rankings for the "High income: OECD" and "High income: nonOECD" groups? 
  * Plot the GDP for all of the countries. Use ggplot2 to color your plot by Income Group
  * Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle 
    income but among the 38 nations with highest GDP

# Introduction
 This will present data of how GDP and education data go something....etc
 
```{r}

# First need to download the files

CaseStudy_1 <- read.csv("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv")
CaseStudy_2 <- read.csv("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv")

```

# Next will be the tidying and merging data code

```{r}
# first need to look at how it is set up
CaseStudy_1
str(CaseStudy_1)
names(CaseStudy_1)
CaseStudy_2
str(CaseStudy_2)
names(CaseStudy_2)
```

# The code to answer the five questions

```{r}

# Question 1 is....

# The code for question 1

# The answer is

```

# Plots

```{r}

x <- c(2,4,6,9,22,33,44)

y <- c(33,4,55,6,8,9,32)

plot(x, y)


```

# Conclusion
 This is the best most greatest case study ever in the history of man kind!

