---
title: "Week4 Homework, 2016-0509 MSDS 6306"
author: "Christopher Farrar"
date: "May 28, 2016"
output: 
   html_document:
   keep_md: true
   
---
# Week 4 Homework
  * Write a bootstrap code to illustrate the central limit theorem in R markdown and push the results
    to GitHub
  * Use a normal distribution with two different sample sizes
  * Use a exponential distribution with two different sample sizes
  * Comment on the code and explain the results
  * Deliverable is a link to the GitHub repo containing the code

## Normal distribution with bootstrap code 

```{r}
x <- rnorm(18, 4, 2)
y <- rnorm(9, 4, 2)

normsampleA <- sample(x, size = length(x), replace = TRUE)

normsampleB <- sample(y, size = length(y), replace = TRUE)

Z <- 1000

sampleAmedian <- numeric(Z)
sampleBmedian <- numeric(Z)

for (i in 1:Z) {
  normsampleA <- sample(x, size = length(x), replace = TRUE)
  normsampleB <- sample(y, size = length(y), replace = TRUE)
  sampleAmedian[i] <- median(normsampleA, na.rm = FALSE)
  sampleBmedian[i] <- median(normsampleB, na.rm = FALSE)
}
sampleAmedian
sampleAmedian

hist(sampleAmedian)
hist(sampleBmedian)

```

## Exponential distribution with bootstrap code

```{r}

A <- c(2.1,4.3,2.8,6.4,3.6,3.3,7.2)
B <- c(3.1,2.0,4.4,6.0,1.2)

expsampleA <- sample(A, size = length(A), replace = TRUE)
expsampleB <- sample(B, size = length(B), replace = TRUE)

expA <- pexp(A, rate = 1, lower.tail = TRUE, log.p = FALSE)
expB <- pexp(B, rate = 1, lower.tail = TRUE, log.p = FALSE)

median(expA, na.rm = FALSE)
median(expB, na.rm = FALSE)

Z <- 1000

expAmedian <- numeric(Z)
expBmedian <- numeric(Z)

for (i in 1:Z) {
  expsampleA <- sample(x, size = length(x), replace = TRUE)
  expsampleB <- sample(y, size = length(y), replace = TRUE)
  expAmedian[i] <- median(expsampleA, na.rm = FALSE)
  expBmedian[i] <- median(expsampleB, na.rm = FALSE)
  }
expAmedian
expBmedian

hist(expAmedian)
hist(expBmedian)

```

## Summary 
  * "The central limit theorem asserts that averages based on large samples have approximately normal
    sampling distributions, regardless of the shape of the population distribution. This suggests
    that underlying normality is not a serious issue, as long as sample sizes are reasonably large" 
  
  * This is to suggest that as we have different small sample sizes, if we run the bootstrap...to
    extrapolate the values to a large sample size. The values will follow a normal standard
    distribution based on the central limit theorem   